Visual Diagnostics of a Model Explainer -- Tools for the Assessment of LIME Explanations

### 2020-09-18 paper.Rnw
one small change to code in paper (removed unnecessary line) and reran everything

  # Apply lime with various input options to the hamby data
  bullet_lime_explain_noperms <- apply_lime(
    train = bullet_train %>% 
      arrange(rfscore) %>% 
      select(all_of(bullet_features)),
    test = bullet_test %>%
      select(all_of(bullet_features)) %>%
      na.omit(),
    model = bulletxtrctr::rtrees,
    label = as.character(TRUE),
    n_features = 3,
    sim_method = c('quantile_bins', 'equal_bins',
                   'kernel_density', 'normal_approx'),
    nbins = 2:6,
    feature_select = "auto",
    dist_fun = "gower",
    kernel_width = NULL,
    gower_pow = c(0.5, 1, 10),
    return_perms = FALSE,
    all_fs = FALSE,
    seed = 20190914)

>>>>

  # Apply lime with various input options to the hamby data
  bullet_lime_explain_noperms <- apply_lime(
    train = bullet_train %>%
      select(all_of(bullet_features)),
    test = bullet_test %>%
      select(all_of(bullet_features)) %>%
      na.omit(),
    model = bulletxtrctr::rtrees,
    label = as.character(TRUE),
    n_features = 3,
    sim_method = c('quantile_bins', 'equal_bins',
                   'kernel_density', 'normal_approx'),
    nbins = 2:6,
    feature_select = "auto",
    dist_fun = "gower",
    kernel_width = NULL,
    gower_pow = c(0.5, 1, 10),
    return_perms = FALSE,
    all_fs = FALSE,
    seed = 20190914)
